\input{common/standard_preamble}

\title{
\Huge Remote Launch Control System Setup\\
\vspace{1cm}
\Large For UXO CF5}


\begin{document}



\input{common/standard_titlepage}

\section{Remote Launch Control System Setup Procedure}

% begin operators declarations (for buttons) -- {{{
\operator{priarm}{red}{Primary Ignition Arm}{Primary Arm Missile Switch}
\operator{secarm}{red}{Secondary Ignition Arm}{Secondary Arm Missile Switch}
\operator{fire}{red}{Fire}{Big Red Fire Button}
\operator{inj}{red}{Disconnect}{Disconnect Missile Switch}
\operator{rfill}{Green}{Fill}{Remote Fill Missile Switch}
\operator{rvent}{blue}{Tank Vent}{Remote Tank Vent Missile Switch}
% end operators declarations (for buttons) -- }}}

% begin contents subsection -- {{{
\subsection{Contents}
This document contains the following:
\begin{itemize}
    \item Inside Setup and checks
    \item Outside Setup
    \item Outside System Checks
\end{itemize}
% end contents subsection -- }}}

% begin required items section -- {{{
\subsection{Required Items}
Things you'll need to perform this procedure
\begin{checklist}
    \item Client Side Box (yellow pelican case)
    \item Tower Side Box (silver briefcase thing)
    \item Three (3) Lithium Polymer 12V batteries
    \item Multimeter (for troubleshooting)
    \item Electrically actuated valve for inside setup
\end{checklist}
% end required items section -- }}}

% begin Inside Setup section -- {{{
\subsection{Inside Setup}
Do what you can inside to keep yourself from frostbite as much as possible.
\begin{checklist}
    \item Put two LiPo batteries in tower side box, in the white 3d printed 
battery holders.
    \item Make sure the actuator switch is off (big black one with a 1 and 0
painted on it), clicked to "0".
    \item Plug in both batteries. Lights on arduino should light up, relays
should click.
    \item Wire electric valve into the connector labelled fill on the tower
side box.
    \item Turn on actuator switch (the black one on the tower side box):
    \begin{checklist}
        \item If remote valve previously wasn't closed, it should now close. If 
not, go to troubleshooting guide.
    \end{checklist}
    \item Put battery in client side box. It plugs into the deans connector
underneath the cutout, and isn't secured to anything.
    \item Turn on client side box (flip power switch).
    \begin{checklist}
        \item Confirm that LCD lights up.
    \end{checklist}
    \item Turn keyswitch 90 degrees clockwise.
    \begin{checklist}
        \item Confirm that missile switches light up.
    \end{checklist}
    \item Flip \rfill{} missile switch
    \begin{checklist}
        \item Confirm that Electrically actuated valve turns to open
    \end{checklist}
    \item Unflip \rfill{} missile switch
    \begin{checklist}
        \item Confirm that Electrically actuated valve turns to close
    \end{checklist}
    \item Disconnect electrically actuated valve from RFV relay board
\end{checklist}

End inside checks

% end Inside Setup section -- }}}

% begin Outside Setup section -- {{{
\subsection{Outside setup}
\begin{checklist}
    \item Find a good spot to put the tower side box. Put the tower side box there
    \item Connect remote fill valve to the connector labelled Fill on the tower
side box
    \item Connect remote vent valve to the connector labelled Vent on the tower
side box
    \item Connect injector valve to the connector labelled Disconnect on the tower
side box
    \item Perform "Outside Checks" Procedure
    \item Disconnect both LiPos in tower side box to conserve power
    \item Turn off client side box to conserve power
\end{checklist}
End of setup procedure
% end Outside Setup section -- }}}

% begin Outside checks section -- {{{
\subsection{Outside Checks}
Perform during outside setup procedure and again immediately before test
\begin{checklist}
    \item Turn on client side box (Ensure LCD lights up)
    \item Turn key switch (Ensure missile switches light up)
    \item Turn on tower side box actuator switch
    \item Confirm that all three electrically actuated valves are closed
    \item Flip \rfill{} missile switch
    \begin{checklist}
        \item Confirm that remote fill valve opened
    \end{checklist}
    \item Un-flip \rfill{} switch
    \begin{checklist}
        \item Confirm that remote fill valve closed
    \end{checklist}

    \item Flip \rvent{} missile switch
    \begin{checklist}
        \item Confirm that remote vent valve opened
    \end{checklist}
    \item Un-flip \rvent{} switch
    \begin{checklist}
        \item Confirm that remote vent valve closed
    \end{checklist}

    \item Flip \inj{} missile switch
    \begin{checklist}
        \item Confirm that injector valve opened
    \end{checklist}
    \item Un-flip \inj{} switch
    \begin{checklist}
        \item Confirm that injector valve closed
    \end{checklist}
\end{checklist}
End of Checks procedure
% end Outside checks section -- }}}



\end{document}
